Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Rename prototype solution factor from psi_0 to chi

\item Replace $\psi_0$ with $\chi$.

@@

\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
Let
\[ \psi_0(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
so $\solproto = \frac{p(b)}{p} \psi_0$. Observing that $d\psi_0 = -\frac{q}{p} \psi_0\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\psi_0$. For each $a \in \Omega$, we have
\begin{align*}
\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0 \\
& = \frac{p(b)}{p(a)} \left[ \psi_0(a) - \lim_{\zeta \to 0} \psi_0 \right] \\
& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \psi_0.
\end{align*}
Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \psi_0 = 0$.

By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:limit_h1}
\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right| < C
\end{equation}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\psi_0$:
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \psi_0 = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\end{proof}

@@

\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]

@@

\begin{align*}
|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
&  \lesssim |\zeta(a)|^{\tau-1}.
\end{align*}

@@

Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < C \]
in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $\alpha \in \domain_\text{near}$, the integral
\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
converges, allowing us to write
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta - \alpha|$ in $\domain_\text{near}$, implying that
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta - \alpha|\big) \Big] \]
when we restrict to $\domain_\text{near}$.

>>>>

\item \textcolor{gray}{Replace $\psi_0$ with $\chi$.}

@@

\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
Let
\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
so $\solproto = \frac{p(b)}{p} \chi$. Observing that $d\chi = -\frac{q}{p} \chi\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\chi$. For each $a \in \domain$, we have
\begin{align*}
\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\chi\;d\zeta \\
& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \chi\;d\zeta\\
& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
& = \frac{p(b)}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \chi.
\end{align*}
Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \chi = 0$.

By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:limit_h1}
\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right| < C
\end{equation}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\end{proof}

@@

\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]

@@

\begin{align*}
|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(b)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
&  \lesssim |\zeta(a)|^{\tau-1}.
\end{align*}

@@

Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < C \]
in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $a \in \domain_\text{near}$, the integral
\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
converges, allowing us to write
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta - \alpha|$ in $\domain_\text{near}$, implying that
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta - \alpha|\big) \Big] \]
when we restrict to $\domain_\text{near}$.
